### 2021-03-18 paper.Rmd
huber plot

Some notations are defined for describing $d$-dimensional projections in $p$-dimensional space. Let $X_{n \times p}$ be the original data whose projections are of our interest. A projection basis, $A_{p \times d}$, characterises the direction from which the high-dimensional data are projected. Projection bases needs to satisfy an orthonormality condition, which requires each axis to be unit vector and perpendicular to each other, and this gives the basis space a geometrical structure of a Stiefel manifold. With a data matrix and a projection basis, a projection can be defined as $Y = X \cdot A$ for visual inspection.

> figure 2 diagram illustrating a projection: Di thinks making a Huber plot (2D data - 1D projection) here with projected data on a couple of directions is ideal
```{r, eval = FALSE}
PPtreeViz::Huberplot(iris[,1:2],iris[,5],PPmethod="LDA")
```

>>>>

Below introduces the notations used for describing $d$-dimensional projections in a $p$-dimensional space. Let $X_{n \times p}$ be the data whose projections are of interest. A projection basis, $A_{p \times d}$, characterises the direction from which the data are projected and needs to satisfy an orthonormality condition, which requires each column to be a unit vector and to be perpendicular to each other. This condition gives the $p$-dimensional basis space a geometrical structure of a Stiefel manifold. With a data matrix and a projection basis, a projection of the data can be defined as $Y = X \cdot A$. Figure \ref{fig:notation-huber} shows an example of the 2D iris data (sepal measures only) in a huber's plot, along with a 1D projection in the histogram. This projection is created based on projecting the data onto the solid line in the huber plot and it separates group setosa from versicolor and virginica. (This plot is created with package PPtreeViz, whose reference is @Lee2005-gl)

\begin{figure*}
   \centering
         \includegraphics[width=\textwidth]{figures/notation-huber.pdf}
\caption{Huber's plot (left) of the 2D iris data (sepal length and width only). The solid ellipse represents how well the projection, onto different directions, separates the three species and the dashed circle is a reference guide. The histogram (right) is the 1D projection of the data onto the direction outlined as the solid line in the huber's plot.}
\label{fig:notation-huber}
\end{figure*}
